Analysis2

### 2023-10-24 Lahman Analysis/Rough Analysis 2/Analysis2.qmd
Added comments to Stan and added analyses

@@

ggplot(data = Batting_summary) +
  geom_pointrange(mapping = aes(x = Age, y = prop, ymin = prop - se,
                                ymax = prop + se))
```
Let's graph again, restricting to players aged 20 to 40.

```{r}
ggplot(data = Batting_summary %>% filter(Age >= 20 & Age <= 40)) +
  geom_pointrange(mapping = aes(x = Age, y = prop, ymin = prop - se,
                                ymax = prop + se))
```
Our first model will include a linear term for age and will be restricted to this age range.

@@

```{r}
glm(cbind(HR, AB - HR) ~ c.Age, data = Batting_summary_restricted, family = binomial)
```
And now let's fit using the following simple model:

@@

```{r}
fit_23 <- stan(
  file = "HR23.stan",
  data = data_23
)
```
```{r}
summary(fit_23)$summary %>% signif(3)
```

@@

ggplot(data = sum_2001) + 
  geom_point(mapping = aes(x = Age - 30, y = logit(prop))) +
  geom_abline(slope = post_sample$beta1, intercept = post_sample$"b[29]")
```
Try a new version of the model:

```{r}
sum_all_years <- Batting %>% group_by(yearID, Age) %>%
  summarize(HR = sum(HR), AB = sum(AB))
```

@@

>>>>

```{r}
#Create the summarized data frame

Sum.Batting <- Batting %>% 
  group_by(yearID, Age) %>% 
  summarize(AB = sum(AB),
            HR = sum(HR))
```

@@

ggplot(data = Batting_summary) +
  geom_pointrange(mapping = aes(x = Age, y = prop, ymin = prop - se,
                                ymax = prop + se))
```

Let's graph again, restricting to players aged 20 to 40.

```{r}
ggplot(data = Batting_summary %>% filter(Age >= 20 & Age <= 40)) +
  geom_pointrange(mapping = aes(x = Age, y = prop, ymin = prop - se,
                                ymax = prop + se))
```

Our first model will include a linear term for age and will be restricted to this age range.

@@

```{r}
glm(cbind(HR, AB - HR) ~ c.Age, data = Batting_summary_restricted, family = binomial)
```

And now let's fit using the following simple model:

@@

```{r}
fit_23 <- stan(
  file = "HR23.stan",
  data = data_23
)
```

```{r}
summary(fit_23)$summary %>% signif(3)
```

@@

ggplot(data = sum_2001) + 
  geom_point(mapping = aes(x = Age - 30, y = logit(prop))) +
  geom_abline(slope = post_sample$beta1, intercept = post_sample$"b[29]")
```

Try a new version of the model:

```{r}
sum_all_years <- Batting %>% group_by(yearID, Age) %>%
  summarize(HR = sum(HR), AB = sum(AB), SB = sum(SB))
```

@@

```{r}
data23b <- list(
  N = nrow(sum_all_years),
  n_year = n_distinct(sum_all_years$yearID),
  AB = sum_all_years %>% pull(AB),
  HR = sum_all_years %>% pull(HR),
  Year = sum_all_years %>% pull(yearID) -1972,
  Age = sum_all_years %>% pull(Age) -30
)
```

```{r}
#I find that 500 works and 200 doesn't
fit23b <- stan(
  file = "HR23b.stan",
  data = data23b,
  iter = 500
)
```

```{r}
summary(fit23b)$summary %>% signif(3)
```

Fitting the model but with SB's considered as a proxy or player archetype

```{r}
data24 <- list(
  N = nrow(sum_all_years),
  n_year = n_distinct(sum_all_years$yearID),
  AB = sum_all_years %>% pull(AB),
  HR = sum_all_years %>% pull(HR),
  Year = sum_all_years %>% pull(yearID) -1972,
  Age = sum_all_years %>% pull(Age) -30,
  SB = sum_all_years %>% pull(SB)
)
```

```{r}
fit23b <- stan(
  file = "HR24.stan",
  data = data24,
  iter = 500
)
```

Iterating using both 500 and 1000 loops leaves an error. Suggesting that using SB probably is not a good idea. Or at least we should talk about it more before implementation.
